---
title: "Demonstration of Binomial"
author: "Joseph Hernandez"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### 1. Load the Package 

The binomial package is an R package with functions for calculating the probabilities of a Binomial random variable and related calculations such as the probability distribution (cumulative and not), expected value, variance, skewnness, and others. Most *binomial* functions call some combination of *trials (n)*, *prob (p)*, and *success (k)*; these correspond to the trials undergone, probability of success, and number of successes respectively. 

```{r, echo=FALSE, eval = TRUE, message=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
library(ggplot2)
```

### 2. Functions
The following functions are part of *binomial*: 

```{r eval = FALSE}
bin_choose()       # returns number of combinations where k successes can occur in n trials
bin_probability()  # returns the probability of k successes in n trials with a given probability
bin_distribution() # returns distribution of the probabilities of a binomial random variable
bin_cumulative()   # returns the cumulative distribution of the probabilities of a binomial random variable
bin_variable()     # returns a binomial random variable and summary statistics
bin_mean()         # returns the expected value of k and n 
bin_mode()         # returns the mode of k and n  
bin_variance()     # returns the variance of k and n
bin_skewness()     # returns the skewness of k and n  
bin_kurtosis()     # returns the kurtosis of k and n 
```

### 3. Examples and Uses 

The aforementioned functions are used in the following ways: 

##### bin_choose()

This function returns number of combinations where k successes can occur in n trials. 
```{r}
bin_choose(n = 5, k = 2)
```

##### bin_probability()

This function returns returns the probability of k successes in n trials with a given probability
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

##### bin_distribution()

This function returns a distribution, as a dataframe of class data.frame and *bindis*, of the probabilities of a binomial random variable.
```{r}
bindis1 <- bin_distribution(trials = 5, prob = 0.5)
bindis1
```

A data.frame object of class *bindis* will become a visual plot as such: 
```{r}
plot(bindis1)
```

##### bin_cumulative()

This function returns another type of distribution, as a dataframe of class data.frame and *bincum*, of the probabilities of a binomial random variable and the cumulative probabilities of a binomial random variable distribution.
```{r}
bincum1 <- bin_cumulative(trials = 5, prob = 0.5)
bincum1
```

A data.frame object of class *bincum* will become a visual plot as such: 
```{r}
plot(bincum1)
```

##### bin_variable()

This function returns returns a binomial random variable of class *binvar* and related summary statistics and parameters. 
```{r}
binvar1 <- bin_variable(trials = 5, prob = 0.5)
binvar1
```

A *binvar* object will print as: 
```{r}
print(binvar1)
```

Running summary() on a *binvar* object will return a special printed output of the measures and parameters of the object: 
```{r}
summary(binvar1)
```

##### bin_mean()

This function is a measure of the binomial random varaible that returns the variable's expected value: 
```{r}
bin_mean(trials = 6, prob = 0.5)
```

##### bin_mode()

This function is a measure of the binomial random varaible that returns the variable's modal value: 
```{r}
bin_mode(trials = 6, prob = 0.5)
```

##### bin_variance()

This function is a measure of the binomial random varaible that returns the variable's variance or the varaince of the expected distribution: 
```{r}
bin_variance(trials = 6, prob = 0.5)
```

##### bin_skewness()

This function is a measure of the binomial random varaible that returns the variable's skewness or the skewness of the expected distribution: 
```{r}
bin_skewness(trials = 6, prob = 0.5)
```

##### bin_kurtosis()

This function is a measure of the binomial random varaible that returns the variable's kurtosis or the kurtosis of the expected distribution: 
```{r}
bin_kurtosis(trials = 6, prob = 0.5)
```


